---
title: "GENEration"
author: "Oswin"
output: pdf_document
---

This script is user-friendly. 
You don't need to use code. 
Please follow each step. 

---

# 0) Start up and install any missing packages

To change how long the messages are displayed for, change 
message.delay.time <- 3
to a bigger (slower) or smaller (faster) number.

To eliminate messages and just respond to prompts, set
Be.Chatty <- TRUE
to FALSE rather than TRUE in the gray box below.

This section installs any packages you will need for the analysis.
You'll get a warning if anything fails to install properly. 


```{r Set parameters}
abundance.dir <- # pathway of your abundance folder 
geneset.dir <- "./GeneSet"
message.delay.time <- 1
Be.Chatty <- TRUE
paired = TRUE
set.seed(12345)

source( "./Functions/0.startup.R" )
```

# 1) Load packages and source files

```{r Load packages, warning=F, message=F}
source( "./Functions/1.load_runchecks.R")
```

# 2) Set Condition

```{r Load packages}
source( "./Functions/2.set_group.R")
```


# 3) Check data 

```{r}
source( "./Functions/3.check_data.R")
```

# 4) Generate gene expression

```{r, warning=F, message=F}
source( "./Functions/4.generate_gene_expression.R")
```


# 5) DGE

```{r}
source( "./Functions/5.DGE.R")
```

# 6) Plot 


```{r, warning=F, fig.width=5, fig.height=4}
source( "./Functions/6.plot.R")
```


```{r, warning=F}
source( "./Functions/7.GSEA.R")
```


```{r}
sessionInfo()
```







